\acknowledgements{%
I'd first like to thank my thesis advisor, Prof.~Edgar Choueiri.
Thank you for this opportunity to learn and grow as a researcher, and for helping me to keep the big picture in mind when I would invariably get bogged down in the details of my work.
I'd also like to acknowledge the support and feedback of my thesis committee, Profs.~Clarence Rowley and Bede Liu; the assistance and guidance of various technical staff (Bob and Chris in particular) who have come and gone from the lab; the help and camaraderie of my EP lab counterparts; and the mentorship of Prof.~Braxton Boren, former postdoc, reader of this thesis, and honorary fourth member of my committee.

Thanks also to my family for their support and encouragement throughout the years.
Thank you, Mom and Dad, for your wise counsel and/or your willingness to put up with my griping;
Ben and Diana, for reminding me that there are important things in life outside of work;
and Tomas and Isabel for your unbounded enthusiasm for playing hide-and-seek -- I look forward to playing again soon.
I'd also like to thank my chosen second family, Nina and Juno.
Nina, I hope you know how invaluable your support has been to this process.
Thank you for sticking with me through some difficult times for both of us.
Juno, thank you for being a limitless source love and joy, and for giving me a reason to pause my work and actually get some exercise.

And of course, to my third family, my housemates of Local 315.
Without you all in my life, I seriously wonder if I would have seen any other humans (outside of the lab) these last few years.
Thank you all for helping(/forcing) me to have some fun once in a while, and for your endless support.
If any of you ever want to meet up for brunch, board games, X-Files, or naan-nini's, count me in.

Finally, Rahul, I can't thank you enough for going through this process with me.
I likely would have gone insane by myself in the lab, so thank you for your partnership.
But also, and more importantly, thank you for your friendship; working with you has made the rough times tolerable and the good times significantly more fun.
Don't forget: we still need to patent that alignment technique, but maybe finish your thesis first.

This project was sponsored by the Sony Corporation of America.
Additional financial support was provided by research grants from Focal and Tesla.
This dissertation carries T\#3378 in the records of the Department of Mechanical and Aerospace Engineering. % must be the final sentence
}